The Heavy Photon Search Test Detector

### 2014-04-30 author_list_hps_PAC39_compact.tex
Added author list from PAC39 report.
New abstract, edited intro, overview, beamline and the start of SVT
Separate authors
Comments from Raphael Dupre on draft v2.
Adding more changes suggested by Larry Weinstein to 2nd draft.
New author list from EC.

\newcommand{\red[1]}{{\color{red}{\bf #1}}}
\newcommand{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand{\CUA}{Catholic University of America, Washington, D.C. 20064}
\newcommand{\OU}{Ohio University,  Athens, Ohio 45701}
\newcommand{\YEREVAN}{Yerevan Physics Institute, 375036 Yerevan, Armenia}
\newcommand{\SCAROLINA}{University of South Carolina, Columbia, South Carolina 29208}
\newcommand{\NSU}{Norfolk State University, Norfolk, Virginia 23504}
\newcommand{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand{\genova}{Istituto Nazionale di Fisica Nucleare, Sezione di Genova e Dipartimento di Fisica dell\'Universita, 16146 Genova, Italy}
\newcommand{\SACLAY}{CEA, Centre de Saclay, Irfu/Service de Physique Nucl\'eaire 91191 Gif-sur-Yvette, France}
\newcommand{\ORSAY}{Institut de Physique Nucleaire d'Orsay, IN2P3, BP 1, 91406 Orsay, France}
\newcommand{\ECOLE}{CPhT, Ecole Polytechnique, F 91128 PALAISEAU CEDEX, France}
\newcommand{\UCSC}{University of California, Santa Cruz, CA 95064}
\newcommand{\SUNY}{Stony Brook University, Stony Brook, NY 11794-3800}
\newcommand{\FNAL}{Fermi National Accelerator Laboratory, Batavia, IL 60510-5011}
\newcommand{\HUJ}{Hebrew University of Jerusalem, Jerusalem, Israel}
\newcommand{\UNH}{University of New Hampshire, Department of Physics, Durham, NH 03824}
\newcommand{\PERIMETER}{Perimeter Institute, Ontario, Canada N2L 2Y5}
\newcommand{\RPI}{Rensselaer Polytechnic Institute, Department of Physics, Troy, NY 12181}
\newcommand{\SLAC}{SLAC National Accelerator Laboratory, Menlo Park, CA 94025}
\newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}
\renewcommand*{\thesection}{\arabic{section}}
\newcommand{\Contact}{Contact person}

\begin{document}

\title{\bf\large{Status of the Heavy Photon Search Experiment at Jefferson Laboratory}}
\author{P. Hansson Adrian, C. Field, N. Graf, M. Graham, G. Haller, R. Herbst, J. Jaros\footnote{Co-spokesperson\label{spoks}}, 
T. Maruyama, J. McCormick, K. Moffeit, T. Nelson, H. Neal, A. Odian, M. Oriunno, S. Uemura, D. Walz}
\affiliation{\SLAC}                                 
 \author{A. Grillo, V. Fadeyev, O. Moreno}
\affiliation{\UCSC}
\author{W. Cooper}
\affiliation{\FNAL}
\author{S. Boyarinov, V. Burkert, A. Deur, H. Egiyan, L. Elouadrhiri, A. Freyberger, F.-X. Girod, 
V. Kubarovsky, Y. Sharabian, S. Stepanyan\footref{spoks}, M. Ungaro, B. Wojtsekhowski}
\affiliation{\JLAB}
\author{R. Essig}
\affiliation{\SUNY}
\author{M. Holtrop\footref{spoks}, K. Slifer, S. K. Phillips}
\affiliation{\UNH} 
\author{A. Fradi, B. Guegan, M. Guidal, S. Niccolai, S. Pisano, E. Rauly, P. Rosier and D. Sokhan}
\affiliation{\ORSAY}
\author{P. Schuster, N. Toro}
\affiliation{\PERIMETER}
\author{N. Dashyan, N. Gevorgyan, R. Paremuzyan, H. Voskanyan}
\affiliation{\YEREVAN}
\author{M. Khandaker, C. Salgado}
\affiliation{\NSU}
\author{M. Battaglieri, R. De Vita}
\affiliation{\genova}
\author{S. Bueltmann, L. Weinstein}
\affiliation{\ODU}
\author{G. Ron}
\affiliation{\HUJ}
\author{P. Stoler, A. Kubarovsky}
\affiliation{\RPI}
\author{K. Griffioen}
\affiliation{\WNM}

>>>>

\newcommand{\red[1]}{{\color{red}{\bf #1}}}
\newcommand{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand{\CUA}{Catholic University of America, Washington, D.C. 20064}
\newcommand{\OU}{Ohio University,  Athens, Ohio 45701}
\newcommand{\YEREVAN}{Yerevan Physics Institute, 375036 Yerevan, Armenia}
\newcommand{\SCAROLINA}{University of South Carolina, Columbia, South Carolina 29208}
\newcommand{\NSU}{Norfolk State University, Norfolk, Virginia 23504}
\newcommand{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand{\genova}{Istituto Nazionale di Fisica Nucleare, Sezione di Genova e Dipartimento di Fisica dell\'Universita, 16146 Genova, Italy}
\newcommand{\SACLAY}{CEA, Centre de Saclay, Irfu/Service de Physique Nucl\'eaire 91191 Gif-sur-Yvette, France}
\newcommand{\ORSAY}{Institut de Physique Nucleaire d'Orsay, IN2P3, BP 1, 91406 Orsay, France}
\newcommand{\ECOLE}{CPhT, Ecole Polytechnique, F 91128 PALAISEAU CEDEX, France}
\newcommand{\UCSC}{University of California, Santa Cruz, CA 95064}
\newcommand{\SUNY}{Stony Brook University, Stony Brook, NY 11794-3800}
\newcommand{\FNAL}{Fermi National Accelerator Laboratory, Batavia, IL 60510-5011}
\newcommand{\UNH}{University of New Hampshire, Department of Physics, Durham, NH 03824}
\newcommand{\PERIMETER}{Perimeter Institute, Ontario, Canada N2L 2Y5}
\newcommand{\RPI}{Rensselaer Polytechnic Institute, Department of Physics, Troy, NY 12181}
\newcommand{\SLAC}{SLAC National Accelerator Laboratory, Menlo Park, CA 94025}
\newcommand{\WNM}{The College of William and Mary, Department of Physics, Williamsburg, VA 23185}
\newcommand{\GLASGOW}{University of Glasgow, Glasgow, G12 8QQ, Scotland, UK}
\newcommand{\RUTGERS}{Rutgers University, Department of Physics and Astronomy, Piscataway, NJ 08854}

\author[SLAC]{C. Field}
\author[SLAC]{P. Hansson Adrian\corref{corrauthor}}
\ead{phansson@slac.stanford.edu}
\author[SLAC]{N. Graf} 
\author[SLAC]{ M. Graham} 
\author[SLAC]{ G. Haller} 
\author[SLAC]{ R. Herbst} 
\author[SLAC]{ J. Jaros}
\author[SLAC]{T. Maruyama} 
\author[SLAC]{ J. McCormick} 
\author[SLAC]{ K. Moffeit} 
\author[SLAC]{ T. Nelson} 
\author[SLAC]{ H. Neal} 
\author[SLAC]{ A. Odian} 
\author[SLAC]{ M. Oriunno} 
\author[SLAC]{ R. Partridge} 
\author[SLAC]{ S. Uemura} 
\author[SLAC]{ D. Walz}
%
\author[UCSC]{A. Grillo} 
\author[UCSC]{ V. Fadeyev} 
\author[UCSC]{ O. Moreno}
%
\author[FNAL]{W. Cooper}
%
\author[JLAB]{S. Boyarinov} 
\author[JLAB]{ V. Burkert} 
\author[JLAB]{C. Cuevas}
\author[JLAB]{ A. Deur} 
\author[JLAB]{ H. Egiyan}
 \author[JLAB]{ L. Elouadrhiri} 
 \author[JLAB]{ A. Freyberger} 
 \author[JLAB]{ F.-X. Girod} 
 \author[JLAB]{ S. Kaneta}
 \author[JLAB]{ V. Kubarovsky} 
 \author[JLAB]{ B. Raydo} 
\author[JLAB]{ Y. Sharabian} 
\author[JLAB]{ S. Stepanyan}
\author[JLAB]{ M. Ungaro} 
\author[JLAB]{ B. Wojtsekhowski}
%
\author[SUNY]{R. Essig}
%
\author[UNH]{M. Holtrop}
\author[UNH]{ S. K. Phillips}
%
\author[ORSAY]{ C. Desnault}
\author[ORSAY]{ M. Guidal} 
\author[ORSAY]{ S. Niccolai} 
\author[ORSAY]{ E. Rauly}
\author[ORSAY]{ E. Rindel} 
\author[ORSAY]{ P. Rosier}
 %
\author[PERIMETER]{P. Schuster} 
\author[PERIMETER]{ N. Toro}
%
\author[YEREVAN]{N. Dashyan} 
\author[YEREVAN]{ N. Gevorgyan} 
\author[YEREVAN]{ R. Paremuzyan}
\author[YEREVAN]{ H. Voskanyan}
%
\author[NSU]{M. Khandaker} 
\author[NSU]{ C. Salgado}
%
\author[GENOVA]{M. Battaglieri} 
\author[GENOVA]{ R. DeVita}
%
\author[ODU]{S. Bueltmann} 
\author[ODU]{ L. B. Weinstein}
%
\author[RPI]{A. Kubarovsky}
%
\author[WNM]{K. Griffioen}
%
\author[GLASGOW]{D. Sokhan}
%
\author[RUTGERS]{Y. Gershtein}
\author[RUTGERS]{J. Reichert}

\address[SLAC]{\SLAC}                                 
\address[UCSC]{\UCSC}
\address[FNAL]{\FNAL}
\address[JLAB]{\JLAB}
\address[SUNY]{\SUNY}
\address[UNH]{\UNH}
\address[ORSAY]{\ORSAY}
\address[PERIMETER]{\PERIMETER}
\address[YEREVAN]{\YEREVAN}
\address[NSU]{\NSU}
\address[GENOVA]{\genova}
\address[ODU]{\ODU}
\address[RPI]{\RPI}
\address[WNM]{\WNM}
\address[GLASGOW]{\GLASGOW}
\address[RUTGERS]{\RUTGERS}

\cortext[corrauthor]{Corresponding author.}
